Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-09-03 reanalysis-4-propensity_scores.qmd
final
cluster issues

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "test"  # Should match imputation mode

# PARALLEL PROCESSING CONFIGURATION
max_cores_for_ps <- 2  # Maximum cores to use for propensity score estimation (reduced for memory management)

>>>>

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "final"  # Should match imputation mode

# PARALLEL PROCESSING CONFIGURATION
max_cores_for_ps <- 1  # Maximum cores to use for propensity score estimation (reduced for memory management)
